Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-08 paper/paper.tex
another pass on III.C

\Fix{do the same as above for coverage-based fuzzing}

\Fix{do the same as above for black-box fuzzing}

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued by our team
    24, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Priority & Seed \\
    \midrule    
    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978} & HI & webkit.jstests.es6 \\ 
    2  & 4/12 & radamsa & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979} & HI & webkit.jstests.es6 \\
    3  & 4/14 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}  & HI & webkit.jstests.es6    \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749} & HI & JerryScriptjs.ecma      \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033} & HI & mozilla      \\
    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038} & HI & JerryScriptjs.ecma   \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065} & HI & mozilla
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} & \multirow{2}{*}{HI} & \multirow{2}{*}{mozilla}\\
                        &  &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}  &   & \\
    \midrule    
    9  & 4/29 & radamsa & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}  & HI  & JerryScriptjs.ecma\\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} & \multirow{2}{*}{HI} & \multirow{2}{*}{tinyjs.tests}\\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156} &  & 
    \\
    \midrule    
    11 & 5/02 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197} & LO & mozilla \\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208} & HI & mozilla \\
    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} & HI & JerryScriptjs.regression \\
    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} & HI & v8.test.benchmarks\\
    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} & HI & webkit.jstests.es6\\
    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} & LO & mozilla\\
    17 & 5/24 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943} & HI & webkit.jstests.es6\\
    18 & 6/26 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042} & HI & JerryScriptjs.regression\\
    19 & 6/28 & \crossmark & Chakra & Confirmed  & \href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388} & HI & webkit.jstests.es6\\
   \bottomrule     
  \end{tabular}
\end{table*}

>>>>

\Mar{------------ estou aqui -M}

\Fix{quick on mutational fuzzers}

Coverage-based fuzzers like American Fuzz Loop (AFL)~\cite{afl} and
libfuzzer~\cite{libfuzzer} run tests inputs in coverage-instrumented
versions of the program under testing. The typical approach to input
generation of this kind of fuzzer is evolutionary--they try to
minimize the distances to still uncovered branches of the
program. AFL, for instance, takes the instrumented program binary and
one input seed and produces on output crash inputs. Considering our
context of application, we needed to build one runtime engine to
collect coverage information for fuzzing; we chose v8. (There are
options in LLVM clang for that~\cite{libfuzzer}.)  Unfortunately, we
found that most of the inputs produced violate the JS grammar and the
fuzzing task can take days even when considering one seed. That
happens because the entire decision tree of the engine is explored,
including the branches associated with the lexer and parser. For this
reason, Google promotes the creation of fuzz targets associated with
specific program functions. Although that approach has shown very
effective, it requires domain knowledge to create the calling context
for the fuzz target. For those reason, coverage-based fuzzers were not
considered in this study.

\Fix{...do the same as above for black-box fuzzing. explain what kinds of
inputs they can generate.}

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued by our team since April,
    2018. The analysis of warnings was not uninterrupted.}
  \label{tab:bugs}
  \begin{tabular}{cccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Priority & Seed \\
    \midrule    
    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978} & HI & webkit.jstests.es6 \\ 
    2  & 4/12 & radamsa & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979} & HI & webkit.jstests.es6 \\
    3  & 4/14 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}  & HI & webkit.jstests.es6    \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749} & HI & JerryScriptjs.ecma      \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033} & HI & mozilla      \\
    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038} & HI & JerryScriptjs.ecma   \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065} & HI & mozilla
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} & \multirow{2}{*}{HI} & \multirow{2}{*}{mozilla}\\
                        &  &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}  &   & \\
    \midrule    
    9  & 4/29 & radamsa & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}  & HI  & JerryScriptjs.ecma\\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} & \multirow{2}{*}{HI} & \multirow{2}{*}{tinyjs.tests}\\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156} &  & 
    \\
    \midrule    
    11 & 5/02 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197} & LO & mozilla \\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208} & HI & mozilla \\
    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} & HI & JerryScriptjs.regression \\
    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} & HI & v8.test.benchmarks\\
    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} & HI & webkit.jstests.es6\\
    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} & LO & mozilla\\
    17 & 5/24 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943} & HI & webkit.jstests.es6\\
    18 & 6/26 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042} & HI & JerryScriptjs.regression\\
    19 & 6/28 & \crossmark & Chakra & Confirmed  & \href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388} & HI & webkit.jstests.es6\\
   \bottomrule     
  \end{tabular}
\end{table*}
